Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-28 paper.qmd
Added description for grid configurations

The value for $b_2$ is computed by fixing $b_1$.

>>>>

The value for $b_2$ is computed by fixing $b_1$. Considering the lower bound of the NLDR, $a_1 > 2 \times s_1$ and $a_1 > \frac{1-s_1}{b_1 -1}$. The minimum $a_1$ that satisfies the constraints will be selected. For regular hexagons, $a_2 = \frac{2}{\sqrt(3)}a_1$. Therefore, $a_2$ is computed for the minimum $a_1$. According to the upper bound of the NLDR, $b_2 = \left\lceil\frac{r_2 - s_2}{vs} + 1\right\rceil$, where $vs = \frac{a_2}{2} + \sqrt{{(\frac{a_2}{2})}^2 + {(\frac{a_1}{2})}^2}$.
